---
title: "Airbnb Data Analysis"
author: "Binh Tran"
date: "2/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Research question:

## Loading libraries
```{r}
source('load_libraries.R')
```
## Loading data
```{r}
source('load_data.R')
```
# Define functions
```{r}
basic_eda <- function(data)
{
  glimpse(data)
  print(status(data))
  freq(data) 
  print(profiling_num(data))
  plot_num(data)
  describe(data)
}
```
#Initial look at the data
```{r}
# Fetch listings information
str(listings)
```
```{r}
# Display number of rows and columns
cat("Number of rows: ", nrow(listings),"\n")
cat("Number of columns: ", ncol(listings),"\n")
# Display dimensions
cat("Dimension: ",  dim(listings))
# Display columns name
names(listings)
```
The listings dataframe has 22552 rows and 16 columns.
```{r}
#Calculate number of NULL rows
na_count_listings <- sapply(listings, function(y) sum(length(which(is.na(y)))))
na_count_listings <- data.frame(na_count_listings)
na_count_listings
```

There are 4 columns with NULL values:

name = 59 rows
host_name = 26 rows
last_reviews = 3,908 rows
reviews_per_month = 3,914 rows
```{r}
#Calculate number of rows with unicode texts
unicode_count_listings <- sapply(listings, function(y) length(which(grepl("[[:cntrl:]]", stringi::stri_enc_toascii(y)) == TRUE)))
unicode_count_listings <- data.frame(unicode_count_listings)
unicode_count_listings
```
There are 4 columns with unicode texts, which are:

name = 5,477 rows
host_name = 508 rows
neighbourhood_group = 5,654 rows
neighbourhood = 10,377 rows
```{r}
sapply(listings, class)
```
```{r}
summary(listings$price)
```
75% of properties have a price that is $70 or lower and the max price is $9000. There might be outliers.

